The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-08 r_r/manuscript_rihe_r_r.Rmd
add ref, write abstract

@@

We suspect that many universities may have incomplete knowledge about which schools they recruit from and how these schools compare to those they do not recruit from. Our rationale for this statement is that employee turnover in the enrollment management profession is quite high [CITE HOOVER] and many universities rely on expertise from third-party enrollment management consultancies [@list_biz]. Consistent with this idea, when issued public records requests to collect data on "student list" purchases from about 100 public universities [@list_empirics], we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.

>>>>

__ABSTRACT__

Scholarship on nonresident enrollment by public research universities has developed in isolation from scholarship on linkages between private high schools and selective private universities. We argue that these literatures are part of a broader story about the competition for students from affluent schools and communities. This manuscript analyzes off-campus recruiting visits to private high schools made by a convenience sample of 15 public research universities and 14 selective private universities. An off-campus recruiting visit indicates a social relationship between a school and a university. Therefore, we utilize social network methods to examine the recruiting networks of public and private universities. With respect to scale (research question 1), universities in our sample made a disproportionate number of visits to private high schools. With respect to overlap (RQ2), simple network analyses and community detection methods reveal substantial overlap in the recruiting networks of public and private universities. RQ3 assesses the characteristics of visited schools. Both public and private universities tended to visit private schools in their home geographic region and also in the South, where private school enrollment growth has been strongest. Visited private schools enroll a much larger share of white students than visited public schools. Surprisingly, several public research universities visited sectarian private high schools at a rate similar to sectarian private universities.

\pagenumbering{roman}
\newpage
\pagenumbering{gobble}
\pagenumbering{arabic}

@@

We suspect that many universities may have incomplete knowledge about which schools they recruit from and how these schools compare to those they do not recruit from. Our rationale for this statement is that employee turnover in the enrollment management profession is quite high [@em_burnout_hoover] and many universities rely on expertise from third-party enrollment management consultancies [@list_biz]. Consistent with this idea, when issued public records requests to collect data on "student list" purchases from about 100 public universities [@list_empirics], we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.
